
\section{Artifact Replication}
The provided code hosted at \url{https://github.com/megagonlabs/critique-learning} reproduces every quantitative result in the paper, including all tables and numerical claims. It ships (i)~the full pipeline library
(performance agent, critic agent, FAISS + sentence-transformer RAG, all
prompt templates), (ii)~the exact train/test splits used in the paper,
(iii)~the full output logs of every experiment, and (iv)~a single driver
that reproduces all results end-to-end plus one-command analysis scripts
that print every table. The analysis path is self-contained and requires
no API keys; the full re-run calls hosted LLMs via OpenAI and Fireworks.ai.

We are applying for all three badges. The artifact is publicly archived (Available), ships a documented end-to-end pipeline with a minimal working example (Functional), and reproduces every quantitative claim and table in the paper from shipped logs or a full re-run (Reproduced).

Recommended path for reviewers: run E0 (30s, no API access) to verify all claims against shipped logs; optionally run E1 (<10 min, \$0.20) to verify the pipeline is functional. E2 is the full reproduction path but is impractical at ~400h / ~\$600.

\subsection{Description \& Requirements}

\subsubsection{How to access}
The artifact will be archived at Zenodo by the end of artifact evaluation and is currently mirrored at
\url{https://github.com/megagonlabs/critique-learning}.
Licensed under BSD~3-Clause. Dataset splits under \texttt{data\_samples/}
are transformations of upstream datasets and inherit their upstream
licenses; see the repo-level \texttt{README.md}
for per-dataset attribution.

\subsubsection{Hardware dependencies}
No GPU required. All LLM inference is routed to hosted APIs. The only
local model is the sentence-transformer embedder used for RAG
(\texttt{blevlabs/stella\_en\_v5}, $\approx$1.5B~params); CPU execution
works, and \texttt{torch} picks up a GPU automatically if one is present
but there is no GPU-only code path.

\subsubsection{Software dependencies}
Ubuntu~22.04.2, Python~3.10.16, and the pinned package set in
\texttt{requirements.txt}. No containers, privileged
operations, or kernel modules.

\subsubsection{Benchmarks / datasets}
Seven datasets ship pre-split under data\_\allowbreak samples/:
multi\_\allowbreak condition\_\allowbreak ranking\_\allowbreak multichoice,
nfcorpus\_\allowbreak short\_\allowbreak questions, pubmed, and the four
preference tasks \{anime, book, movie, steam\}\_\allowbreak sample\_\allowbreak \{1..10\} (ten independent users each,
averaged in the paper). No downloading required for reproduction.

\subsubsection{API access (re-run experiments only)}
{\small
\begin{itemize}
  \item \texttt{OPENAI\_API\_KEY} --- for \texttt{gpt-4o-mini-2024-07-18} and  
  
        \texttt{gpt-5-2025-08-07}.
  \item \texttt{FIREWORKS\_API\_KEY} (+\texttt{FIREWORKS\_BASE\_URL}) ---
        for \texttt{gpt-oss-20b}, \texttt{llama-4-scout},
        \texttt{qwen3-235b-a22b-instruct-2507},
        \texttt{qwen3-vl-\allowbreak 235b-\allowbreak a22b-thinking}.
\end{itemize}
}
The analysis-only path E0 requires no API access.

\subsection{Installation}
{\small
\begin{verbatim}
git clone https://github.com/megagonlabs/critique-learning.git 
cd critique-learning
python3.10 -m venv .venv
source .venv/bin/activate
pip install -r requirements.txt
\end{verbatim}
}
First invocation downloads and caches the sentence-transformer embedder
via \texttt{huggingface\_hub}.


\subsection{Major claims}
\label{sec:claims}
\begin{description}
\item[C1 (accuracy):] The \texttt{EP+SEM\_CRIT} strategy
yields an average $+8.1$\,pp over zero-shot and $+4.6$\,pp over
label-only RAG (\texttt{EP\_LABEL}) across all six models and seven datasets.
\item[C2 (gain significance):] EP+SEM\_CRIT improves over EP\_LABEL on 32 of 42 (model, dataset) points (sign-test p < 0.001), and over zero\_shot on 38 of 42 points (sign-test p $<$ $10^{-7}$).
\item[C3 (reasoning-token reduction):] On reasoning models, critique-based memory cuts thinking tokens by an average of 31.95\%.
\item[C4 (suggestibility):] Suggestibility scores correlate with EP+SEM\_CRIT gain over zero\_shot (Spearman coefficient=0.402, p=0.008).
\end{description}


All of the above numbers are present verbatim under the \texttt{Summary statistics} section of the report generated by:
\begin{verbatim}
python scripts/reproduce_paper_tables.py
\end{verbatim}

\subsection{Experiments}

\noindent\textbf{E0 (Analysis only; no API access; $\approx$30\,s):}
\begin{verbatim}
python scripts/reproduce_paper_tables.py
\end{verbatim}
prints every table cited in the paper against the shipped log folders: main\_results, train\_size\_ablation, and reflection\_parts\_ablation.
This alone verifies C1--C4 from the provided logs.

\noindent\textbf{E1 (Basic test, $<$10\,min, $\approx$\$0.20)}
\begin{verbatim}
export OPENAI_API_KEY=sk-...
python scripts/run_pipeline.py \
  --dataset data_samples/anime_sample_1 \
  --model  gpt-4o-mini-2024-07-18
python scripts/analyze_logs.py logs/<timestamp>
\end{verbatim}
This runs all five strategies and the consistency probe on one user and
prints an accuracy table, confirming the pipeline is functional.

\noindent\textbf{E2 (Full reproduction from scratch; $\approx$400\,h
wall-clock, $\approx$\$600 API spend):}
\begin{verbatim}
python scripts/run_all_experiments.py
python scripts/reproduce_paper_tables.py \
  --logs logs/<wallclock>
\end{verbatim}
The driver runs all four stages (main pipeline, vary-$K$, train-size
ablation, reflection-parts ablation) of experiments, outputs results into one timestamped directory, and displays results in formats compatible with paper's claims.


\subsection{Comparing to the paper}
Every analyzer prints numbers in the same units, shape, and ordering as
the corresponding paper table, with row/column headers matching the
paper's model and dataset names. 

\begin{verbatim}python scripts/reproduce_paper_tables.py\end{verbatim}
Upon running the above command, all paper claims and tables are recreated from existing logs, and match the numbers presented in the paper exactly.

If re-running experiments, small deviations on rerun experiments from numbers in the paper are expected due to LLM non-determinism
even at temperature~0, particularly on the 25-question preference
splits. However, aggregate claims (C1--C4) are robust.

\subsection{Expected anomalies}
Reasoning-model outputs contain \texttt{ Error: token limit exceeded}
rows; these are counted as wrong by design (see \S "Unusual behavior" in
\texttt{README.md}) and their reduction is itself part of claim C3.

Parse failures return a random wrong answer by design to prevent
malformed JSON responses from silently inflating accuracy.
