\section{Preliminaries}\label{sec:preliminaries}

\subsection{Agent Skills} \label{sec:prelim-skills}
Recent LLM-agent systems commonly treat skills as reusable units of external procedural knowledge that can be retrieved, executed, and updated without modifying the underlying task model. 
Following this practice, let $\pi_{\mathrm{task}}$ denote a frozen task LLM, and let $\mathcal{S}$ be a space of explicit skill artifacts.

\begin{definition}[Agent Skill]
An agent skill is a reusable procedural artifact $s \in \mathcal{S}$ that conditions the execution of the task model on an input instance. 
A skill may encode natural-language instructions, structured workflows, tool-use guidance, or other procedural constraints, while remaining external to the parameters of $\pi_{\mathrm{task}}$.
\end{definition}

Given an instance $x$ and a skill $s$, the frozen task model induces a rollout distribution
\begin{equation} \label{eq:rollout_dist}
\pi_{\mathrm{task}}(\tau \mid x, s),
\end{equation}
where $\tau$ denotes the resulting trajectory. 
In our setting, skills evolve recurrently on the same instance. 
We write $s_g \in \mathcal{S}$ for the skill used at generation $g$, and $\mathcal{H}_g$ for the instance-specific history available up to generation $g$, such as prior rollouts and their verified outcomes. 
These variables will be used to formalize skill evolution in later sections.


\subsection{Group-Relative Policy Optimization} \label{sec:prelim-grpo}
We briefly review Group-Relative Policy Optimization (GRPO) in the language-generation setting, where a policy $\pi_\theta(\cdot \mid x)$ defines a distribution over response rollouts $y$ conditioned on a prompt or context $x \sim \mathcal{D}$. 
GRPO samples a group
\begin{equation} \label{eq:group_sampling}
\mathcal{G}(x)=\{y^{(i)}\}_{i=1}^K,
\qquad
y^{(i)} \stackrel{\mathrm{i.i.d.}}{\sim} \pi_\theta(\cdot \mid x),
\end{equation}
assigns each rollout a verifier score $r(y^{(i)})$, and defines the group-relative advantage
\begin{equation} \label{eq:grpo_adv}
A\!\left(y^{(i)};\mathcal{G}(x)\right)
=
r\!\left(y^{(i)}\right)
-
\frac{1}{K}\sum_{j=1}^K r\!\left(y^{(j)}\right).
\end{equation}
The GRPO objective is
\begin{equation} \label{eq:grpo_obj}
\mathcal{L}_{\mathrm{GRPO}}(\theta)
=
\mathbb{E}_{x \sim \mathcal{D},\, \mathcal{G}(x)}
\left[
\sum_{i=1}^K
A\!\left(y^{(i)};\mathcal{G}(x)\right)
\log \pi_\theta\!\left(y^{(i)} \mid x\right)
\right].
\end{equation}
This group-centered objective promotes rollouts that outperform their peers under the same input context.
